{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-14 paper/paper.tex
give the concurrent state a name

All active\footnote{a thread is active from \texttt{start \textit{pc}} until
it reaches the \texttt{exit} point} threads are collected in a set $Thead$.
The state of the concurrent running threads is defined as the product of
the partial function space $(Thread \rightharpoonup LocState)$ and the set of
global memories $GMemory$. Where $LocState$ is the internal memory of a
thread, from there no information can leak and the $GMemory$ is the critical
part of the system, because it is a memory shared between all active threads.

>>>>

All active\footnote{a thread is active from \texttt{start \textit{pc}} until
it reaches the \texttt{exit} point} threads are collected in a set $Thead$.
The state of the concurrent running threads ($ConcState$) is defined as the
product of the partial function space $(Thread \rightharpoonup LocState)$
and the set of global memories $GMemory$. Where $LocState$ is the internal
memory of a thread, from there no information can leak and the $GMemory$ is
the critical part of the system, because it is a memory shared between all
active threads.
